Proposed Solution

### 2017-01-25 CAV17/secs/intro.tex
stuff

The systems research community has recognized this as an important
problem~\cite{xu16early}. While many efforts have been proposed to check, troubleshoot, diagnose, and repair configuration 
errors~\cite{attariyan10automating,
su07autobash, whitaker04configuration},
those tools mainly try to understand {\emph{what}} caused the 
error -- they are still not on a level of
automatic verification tools used for regular program 
verification~\cite{Leino10Dafny, PiskacWZ14, BobotFMP15} that can
detect errors without executing the code. In this paper we propose
a framework for automated verification of configuration files: we are analyzing 
files and proactively reporting potential errors, without waiting for them to happen. We developed a tool, called \app, and tested it on 
almost a thousand file from Github.

@@

\ruzica{mark, please put here summary of evaluation resuls}

@@

\markk{see above}

datasets. In our verification experiments, 
we first use a public configuration dataset~\cite{configdataset}, which
contains 261 incorrect MySQL configuration files, as our
training set. We then use \app to learn rules from this training set
and refine these rules. Finally, we check sophisticated 
errors of real configuration files crawled from Github,
and detect many errors in these widely-used configuration files.

>>>>

In this paper we propose
a framework for automated verification of configuration files: we are analyzing 
files and proactively reporting potential errors, without waiting for them to happen. We developed a tool, called \app, and tested it on 
almost a thousand file from Github. The systems research community has recognized this as an important
problem~\cite{xu16early}. While many efforts have been proposed to check, troubleshoot, diagnose, and repair configuration 
errors~\cite{attariyan10automating,
su07autobash, whitaker04configuration},
those tools mainly try to understand {\emph{what}} caused the 
error -- they are still not on a level of
automated verification tools used for regular program 
verification~\cite{Leino10Dafny, PiskacWZ14, BobotFMP15} that can
detect errors without executing the code.

@@

@@
